### 2023-12-25 sections/3-datasets.tex
todo note
edits to datasets

All benchmarks were conducted on an Amazon AWS (EC2) \texttt{r6i.16xlarge} instance, with a 64-core Intel Xeon Platinum 8375C CPU 2.90GHz processor, 512GB RAM.
This is the same configuration used in~\cite{Aumller2018ANNBenchmarksAB}
The OS kernel was Ubuntu 22.04.3-Ubuntu SMP. 
The Rust compiler was Rust 1.71.1, and the Python interpreter version was 3.10.12.

\begin{table}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Datasets used in benchmarks.}
    \label{table:datasets:summary}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|l|l|l|}
                    \hline
                    \textbf{Dataset} & \textbf{Distance}  &\textbf{Cardinality}  & \textbf{Dim.}  \\
                    \hline
                    fashion-mnist    & euclidean              & 60,000             & 784       \\
                    \hline 
                    gist             & euclidean              & 1,000,000          & 960       \\
                    \hline
                    glove-25         & cosine              & 1,183,514          & 25        \\
                    \hline
                    glove-50         & cosine              & 1,183,514          & 50        \\
                    \hline
                    glove-100        & cosine              & 1,183,514          & 100       \\
                    \hline
                    sift             & euclidean              & 1,000,000          & 128       \\
                    \hline
                    deep-image       & cosine              & 9,990,000          & 96        \\
                    \hline
                    mnist            & euclidean              & 60,000             & 784       \\
                    \hline
                    lastfm           & cosine              & 292,385            & 65        \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table}

@@

We also benchmarked on a purely random dataset with the same cardinality and dimensionality as sift: 1,000,000 points in 128 dimensions. 
This benchmark allows us to isolate the effect of a manifold structure (which we expect to be absent in a purely random dataset) on the performance of CAKES's algorithms.

\subsection{Silva}
\label{subsec:silva}
Silva 18S~\cite{10.1093/nar/gks1219} contains ribosomal DNA sequences of approximately 2.25 million genomes with an aligned length of 50,000 letters.
We use Levenshtein distance with this dataset.
% I think this needs another sentence but I'm not sure what else to say

\subsection{Radio ML}
The RadioML dataset contains samples of both live and synthetically generated signal captures of different modulation modes over a range of SNR levels. 
Specifically, it is comprised of 24 modulation modes at 26 different SNR levels ranging from -20 dB to 30 dB, with 4,096 samples at each modulation mode and SNR level~\cite{oshea2018radioml}. 
Thus, it contains $24 \cdot 26 \cdot 4096 = 2,555,504$ samples in total. 
Each sample provided in RadioML can be thought of as an array of 2048 floating point values for a single signal capture with labels for SNR and modulation mode.
We use Dynamic Time Warping distance with this dataset.

\label{subsec:radioml}

>>>>

The benchmarks for Fashion-MNIST, Glove-25, Sift and Random (and for their synthetic augmentations) were conducted on an Amazon AWS (EC2) \texttt{r6i.16xlarge} instance, with a 64-core Intel Xeon Platinum 8375C CPU 2.90GHz processor, 512GB RAM.
This is the same configuration used in~\cite{Aumller2018ANNBenchmarksAB}.
The OS kernel was Ubuntu 22.04.3-Ubuntu SMP.
The Rust compiler was Rust 1.72.0, and the Python interpreter version was 3.9.16.

The benchmarks for Silva and RadioML were conducted on an Intel Xeon E5-2690 v4 CPU @ 2.60GHz with 512GB RAM.
The OS kernel was Manjaro Linux 5.15.130-1-MANJARO.
The Rust compiler was Rust 1.72.0, and the Python interpreter version was 3.9.16.

\begin{table}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Datasets used in benchmarks.}
    \label{table:datasets:summary}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|l|l|l|}
                    \hline
                    \textbf{Dataset} & \textbf{Distance}  &\textbf{Cardinality}  & \textbf{Dimensionality}  \\
                    \hline
                    Fashion-Mnist    & Euclidean              & 60,000             & 784       \\
                    \hline
                    Glove-25         & Cosine                 & 1,183,514          & 25        \\
                    \hline
                    Sift             & Euclidean              & 1,000,000          & 128       \\
                    \hline
                    Random           & Euclidean              & 1,000,000          & 128       \\
                    \hline
                    Silva            & Levenshtein            & 2,224,640          & -         \\
                    \hline
                    RadioML          & Dynamic Time Warping   & 97,920             & 1,024     \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table}

@@

For the Random dataset, we used a cardinality of 1,000,000 and a dimensionality of 128 to match the Sift dataset.
This benchmark allows us to isolate the effect of a manifold structure (which we expect to be absent in a purely random dataset) on the performance of the CAKES' algorithms.

\subsection{Silva}
\label{subsec:silva}

Silva 18S~\cite{10.1093/nar/gks1219} contains ribosomal DNA sequences of 2,224,640 genomes with an aligned length of 50,000 letters.
We use Levenshtein distance on unaligned sequences as the distance function for this dataset.
{\color{red} TODO: Define and/or cite Levenshtein distance.}
% I think this needs another sentence but I'm not sure what else to say

\subsection{Radio ML}
\label{subsec:radioml}

The RadioML dataset contains samples of both live and synthetically generated signal captures of different modulation modes over a range of SNR levels.
Specifically, it is comprised of 24 modulation modes at 26 different SNR levels ranging from -20 dB to 30 dB, with 4,096 samples at each modulation mode and SNR level~\cite{oshea2018radioml}.
Thus, it contains $24 \cdot 26 \cdot 4096 = 2,555,504$ samples in total.
Each sample is a 1,024-dimensional complex-valued vector, representing a signal capture (a time series of complex-valued numbers).
We used a subset of this dataset, containing only the 97,920 samples at 10dB SNR.
We use Dynamic Time Warping as the distance function for this dataset.
{\color{red} TODO: Define and/or cite Dynamic Time Warping distance.}
